---
title: "Sevenr Proposal"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

    The source of this data is CORGIS dataset project, which pulled it from the "Million Song Dataset."

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    It was originally collected by Echo Nest, which derived data points about 1 million popular songs. It was collected in 2011. Echo Nest worked in collaboration with LabROSA, which uses intelligent machine listening, enabling the collection of certian data points

-   Write a brief description of the observations.

    In addition to "strings" referencing the names of artists and the style of music with which they are associated, there are many "float" variables to measure things such as how often an artist's songs conform with the style with which they are associated, the average start times of bars and beats in their songs, the loudness of the track, and other variables associated with details of each song.

-   

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    For each of the following music styles---rock, country, and jazz---what variable(s) best explain the 10 most popular songs in that style, and does that variable change depending on the year?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    Different people have different tastes when it comes to music. The goal is to establish what aspect of each genre of music makes it most appealing to listeners of that music, and whether those tastes change. Our hypothesis is that the best explanatory variable changes by year for rock, but not for country and jazz.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    Besides the categorical variables used to identify the song id and genre, the rest of the variables should be quantitative---notably year, level of popularity (which is given on a scale of 0 to 1), tempo, beat interval, etc.

## Literature

"What makes for a hit pop song? What makes for a pop song?

Nicholas Borg and George Hokkanen

<http://cs229.stanford.edu/proj2011/BorgHokkanen-WhatMakesForAHitPopSong.pdf> \

This research article is about the possibility of predicting a hit song based on song features and genre detection. In terms of the data, they took a dataset of 10,000 songs that contained information such as loudness, tempo, key, and other musical features for each song, and they measured the popularity of each song based on the view counts for the song on YouTube. On initial preliminary analysis using basic correlation coefficients, they found that factors like tempo, loudness, and danceability had very weak correlations to song popularity. They faced difficulties because a lot of the variables they measured are largely based on song length, so they had to manipulate the data to normalize this so that the numbers were consistent. They found that there was very little from the audio features of the song that could accurately predict its popularity, and they reasoned that social factors such as the artist's popularity were better predictors. They did have some success at using these factors to predict the song's genre, though, which could be an interesting angle.

Our research question builds on this because we also are looking at various musical features such as pitch, tempo, and loudness and seeing how well they predict a song's popularity based on certain genres. We also are going to see if any of the relationships change based on year too. Hopefully we can reach a better conclusion than the articles and find some interesting connections.

\
\

## Glimpse of data

```{r}
#| label: load-music

music <- read.csv("data/music.csv")
glimpse(music)
```

# Data 2

## Introduction and data

-   Identify the source of the data.

    The variables name, rank, citizenship, countrycode, net worth in billions, self made status, age, source of wealth, and type of wealth are from Forbes. The GDP variable comes from the World Bank World Development Indicators. The rest of the variables are from the author's calculations.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    The data was collected in February 2016 by Caroline Freund and Sarah Oliver at the Peterson Institute for International Economics. It was originally collected by collecting information from Forbes along with other sources for some variables. For others, the author derived values by doing calculations on information from existed variables.

-   Write a brief description of the observations.

    From [source](https://www.piie.com/publications/working-papers/origins-superrich-billionaire-characteristics-database?ResearchID=2917): The data shows that the median age of a company of a European billionaire is nearly 20 years older than that of an American billionaire. Traditional sectors explain more than half of the rise in wealth in Europe; the financial sector and technology-related sectors together are largely responsible for the rise in US wealth.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    Are more billionaires in richer countries self made compared to billionaires in poorer countries?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    The research topic is global billionaire wealth. We want to focus on how inheritance affects wealth, and how different countries have different proportions of self-made billionaires. This can help aid understanding economic inequality within countries and how the wealth of a country can aid or hurt one's ability to become a self-made billionaire. We hypothesize that there will be a higher proportion of self-made billionaires in richer countries compared to billionaires in poorer countries because richer countries may have higher mobility and better education.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    The variables that we would measure to help explain the research question are quantitative and categorical. To measure inheritance, the data set has a categorical variable that measures if the wealth is inherited and how it is inherited if it is. To measure wealth of a country where the billionaire lives, we can measure the GDP of the country, a quantitative variable. To measure wealth, we can measure billionaire rank compared to the rest of the billionaires and their worth in billions which are both quantitative.

## Literature

-   Find one published credible article on the topic you are interested in researching.

    <https://www.tandfonline.com/doi/epdf/10.1080/00472330701822355?needAccess=true&role=button>

-   Provide a one paragraph summary about the article.

    The article discusses the rise of billionaires in several major countries and regions in the world, providing historical, social, and political context. The countries/regions mentioned are Russia, Latin America, China, and India. The major project relevant details are the histories of each region, and if the billionaires inherited their wealth. For example, India is undergoing extreme class polarization; while the billionaires are used as evidence of India's growing wealth, in reality people are growing poorer and poorer. The article also lists the 3 general stages of becoming a billionaire in reference to these regions. What ties the regions together is that they are developing areas; although billionaires are emerging, one cannot conclude that the people themselves are growing wealthier.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    The article only focuses on four regions in the world in relation to wealth of a country and number of billionaires. Our research question aims to expand the scope to the entire world by asking a very similar question, but with all countries in the dataset in mind.

## Glimpse of data

```{r}
#| label: load-billion

billion <- read.csv("data/billionaires.csv")
glimpse(billion)
```

# Data 3

## Introduction and data

-   Identify the source of the data.

    National Survey of Recent College Graduates

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    The data was originally collected in 2010 by the National Science Foundation. They asked individuals in the US under 76 with a college degree obtained within 2-3 years ago about the information that became the variables of the dataset.

-   Write a brief description of the observations.

    There are 517 observations, each of which correspond to a person surveyed. The identifying variables are Year and Education.Major. The other 48 variables include demographic information, salary information, employment status information, and so on.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-graduates

graduates <- read.csv("data/graduates.csv")
glimpse(graduates)
```
