---
title: "Sevenr Project"
subtitle: "Report"
format: html
editor: visual
execute:
  echo: true
---

## Introduction and data

<https://www.piie.com/publications/working-papers/origins-superrich-billionaire-characteristics-database?ResearchID=2917>

Source, topic, when, how, cases, relevant variables

Ethical concerns?

Our research question is: "do the predictors of a linear regression modeling billionaire wealth change depending on if the wealth was inherited or not inherited?" That is, do the factors that are associated with higher levels of billionaire wealth change given that the billionaire had inherited money to begin with or not?

Our hypothesis is that ?

## Methodology

Multivariate linear regression.

Dataset cleaning (lots of 0s for some reason)

Model building

Other tools

## Results

Two (or more) linear regression models

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
library(tidymodels)
```

```{r}
#| label: load-billion

billion <- read.csv("data/billionaires.csv")
#glimpse(billion)
```

```{r}
#| label: data-cleaning

#filtering for year 2001 (not 2014 because of missing gdp info)
billion2001 <- billion |>
  filter(year == 2001) |>
  rename(industry = wealth.how.industry) |>
  mutate(
    industry = if_else(industry == 0, "Other", industry),
    industry = if_else(industry == "Energy" | industry == "Mining and metals", "Energy, mining, and metals", industry),
    industry = if_else(str_detect(industry, "Technology"), "Technology", industry),
    industry = if_else(industry == "Diversified financial", "Money management", industry),
    industry = if_else(industry == "Hedge funds", "Money management", industry),
    industry = if_else(industry == "Venture Capital", "Money management", industry),
    industry = if_else(industry == "Private equity/leveraged buyout", "Money management", industry),
    industry = if_else(industry == "Money Management", "Money management", industry),
    industry = if_else(industry == "Constrution" | industry == "Real Estate", "Real estate, construction", industry)
  )

#var inherited groups inheritance; creating two frames for inherited and not inherited
inheritance_grouping <- billion2001 |>
  mutate(inherited = if_else(str_detect(wealth.how.inherited, "not inherited"), "not inherited", "inherited"))

yes_inherited <- inheritance_grouping |>
  filter(inherited == "inherited")

not_inherited <- inheritance_grouping |>
  filter(inherited == "not inherited")
```

other: 0

construction

consumer

money management: diversified financial, hedge funds, venture capital, private equity/lev buyout

energy: mining and metals

media

non consumer industrial

real estate

retail, restaurant

technology: computer, medical

```{r}
#| label: location-regression

#regression by location.gdp for both groups
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = billion2001) |>
  tidy()
 
billion2001 |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression for location.gdp for inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = yes_inherited) |>
  tidy()
 
yes_inherited |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 

#regression for location.gdp for not inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

```{r}
#| label: sector-regression

#regression by industry for both groups
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = billion2001) |>
  tidy()
 
billion2001 |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression by industry for inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = yes_inherited) |>
  tidy()
 
yes_inherited |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression by industry for not inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

```{r}
#| label: age-regression

#regression by age for both groups
linear_reg() |>
    set_engine("lm") |>
    fit(wealth.worth.in.billions ~ demographics.age, data = billion2001) |>
    tidy()
 
billion2001 |>
    ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
    geom_point() +
    geom_smooth(method = "lm", se = F) 
 
#regression by age for inherited
linear_reg() |>
    set_engine("lm") |>
    fit(wealth.worth.in.billions ~ demographics.age, data = yes_inherited) |>
    tidy()
 
 yes_inherited |>
    ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
    geom_point() +
    geom_smooth(method = "lm", se = F) 
 
#regression by age for not inherited
 linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ demographics.age, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

## Changelog

4/3:

-   filtered year and variables (variable_filter)

-   grouped by inheritance (inheritance_grouping, yes_inherited, not_inherited)

-   regressions by location, age, sector; univariate models from total, then individual group data frames

4/5:

-   renamed variable_filter to billion2001, renamed wealth.how.industry to industry

-   removed selecting variables (aka leaving all variables in)

-   added comments

-   commented out glimpse(billion2001)

-   cleaned up and combined industry levels (check underneath for groupings)

-   changed regression by company.sector to regression by industry

-   
