---
title: "Sevenr Project"
subtitle: "Report"
format: html
editor: visual
execute: 
  echo: true
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
library(tidymodels)
```

# Introduction and data

```{r}
#| label: load-billion
billion <- read.csv("data/billionaires.csv")

glimpse(billion)
```

The dataset we are working with is a large listing of billionaires across the world along with information about them collected at three different time points. There are 2614 observations and 22 variables. Not every observation is a unique billionaire; many are repeated up to three times (one at each time point). In addition, not every 22 variable is statistically interesting; many, such as name, rank, and company.name are identifying variables. However, the other variables are statistically useful and interesting, and our goal is to investigate them.

The dataset was created in 2016 by Caroline Freund and Sarah Oliver, who are (or were) researchers at the Peterson Institute for International Economics. They compiled the list of individuals from Forbes billionaire lists dating from 1996 to 2015. A large percentage of the additional information collected was publicly available, coming from sources such as Forbes, news articles, and company websites.

One caveat about this dataset, and any data categorizing wealth, is that defining wealth is a subjective matter. For example, Forbes had to make many choices in determining who to include in the lists used as sources for this dataset. One such choice was to exclude billionaires that obtained wealth from official positions (e.g. high government roles, state leader positions, etc.). Another choice was to exclude billionaires who obtained their wealth via illegal methods. In addition, individuals and companies may fabricate what they publish about themselves, or simply characterize themselves subjectively. Thus, when drawing conclusions from analysis of this dataset, we must be careful not to generalize statements about legal nonpolitical billionaires to any person on the planet who accumulates wealth.

#### Relevant variables

As mentioned, there are 22 variables, of which some are identifying variables, and the rest are more useful or interesting. They are listed in the table:

| Variable name (unmodified) | Meaning                                                                        |
|--------------------|----------------------------------------------------|
| company.relationship       | relationship to the company (founder, etc.)                                    |
| company.sector             | the sector of the economy to which the business belongs                        |
| company.type               | type of business of the company                                                |
| demographics.age           | age of the individual                                                          |
| location.citizenship       | name of the country for which the individual has citizenship                   |
| location.country.code      | 3-letter country code for which the individual has citizenship                 |
| location.gdp               | gross domestic product of the country for which the individual has citizenship |
| location.region            | part of the world where the individual lives                                   |
| [*wealth*]{.underline}     | [*net worth of the individual in billions of USD*]{.underline}                 |
| wealth.how.category        | where the individual's money came from                                         |
| wealth.how.industry        | the specific industry the individual profited from                             |
| wealth.how.inherited       | whether the individual's wealth was inherited or not                           |
| wealth.how.was.founder     | whether the individual founded their company or not                            |

Of these variables, the wealth variable (underlined and italicized) makes for an interesting response variable; that is, we are interested in seeing how this variable could possibly be affected by the other variables. One variable we are especially curious about exploring, given today's discourse about where wealth comes from, is wealth.how.inherited; do the billionaires who inherit some wealth to begin with accumulate more differently from those who are "self-made"?

#### Literature Review

<https://www.tandfonline.com/doi/epdf/10.1080/00472330701822355?needAccess=true&role=button>

The article discusses the rise of billionaires in several major countries and regions in the world, providing historical, social, and political context. The countries/regions mentioned are Russia, Latin America, China, and India. The major project relevant details are the histories of each region, and if the billionaires inherited their wealth. For example, India is undergoing extreme class polarization; while the billionaires are used as evidence of India's growing wealth, in reality people are growing poorer and poorer. The article also lists the 3 general stages of becoming a billionaire in reference to these regions. What ties the regions together is that they are developing areas; although billionaires are emerging, one cannot conclude that the people themselves are growing wealthier.

The article only focuses on four regions in the world in relation to wealth of a country and number of billionaires. Our research question aims to expand the scope to the entire world by asking a very similar question, but with all countries in the dataset in mind.

#### Research question and hypothesis

Thus, our research question is: what is the best model for predicting billionaire wealth? That is, what variables would be included in a multivariate linear regression with wealth.in.billions as the response variable?

Our hypothesis is that variables such as wealth.how.category, location.gdp, wealth.inherited, and age will be included, as those seem to be pertinent to wealth accumulation.

<https://www.piie.com/publications/working-papers/origins-superrich-billionaire-characteristics-database?ResearchID=2917>

# Methodology

#### Data cleaning

Before any analysis, the dataset was tidied up.

We filtered for a single year instead of working with the data over time to avoid complications. We chose the year 2001, because of the other variables, location.gdp was of interest, and 2001 is the most recent year for which there is data on GDP across the world (there is no GDP data for 2014). The variable wealth was also renamed to just wealth.

```{r}
#| label: filter-2001

billion |> 
  group_by(year) |> 
  summarize(mean_gdp = mean(location.gdp))

billion2001 <- billion |>
  filter(year == 2001) |>
  rename(wealth = wealth.worth.in.billions)
```

Another variable that is of interest is wealth.how.industry, whose values are strings representing the industries that made the billionaires wealthy. After renaming the variable, we combined related industries together. For example, "Venture capital", "Hedge funds", "Diversified financial", and "Private equity/leveraged buyout" all fit into the "Money management" industry.

```{r}
#| label: clean-industry

billion2001 <- billion2001 |>
  rename(industry = wealth.how.industry) |>
  mutate(
    industry = if_else(industry == 0, "Other", industry),
    industry = if_else(industry == "Energy" | industry == "Mining and metals", "Energy, mining, and metals", industry),
    industry = if_else(str_detect(industry, "Technology"), "Technology", industry),
    industry = if_else(industry == "Diversified financial", "Money management", industry),
    industry = if_else(industry == "Hedge funds", "Money management", industry),
    industry = if_else(industry == "Venture Capital", "Money management", industry),
    industry = if_else(industry == "Private equity/leveraged buyout", "Money management", industry),
    industry = if_else(industry == "Money Management", "Money management", industry),
    industry = if_else(industry == "Constrution" | industry == "Real Estate", "Real estate, construction", industry),
    industry = if_else(industry == "Consumer" | industry == "Retail, Restaurant", "Consumer goods, retail, restaurants", industry)
  )
```

demographics.age is another interesting variable; however, several billionaires have an age of 0 listed, which meant some had died before 2001. Because researching dozens of individual death dates or ages demands excessive effort, we decided to filter out any age with 0.

```{r}
#| label: clean-age

billion2001 <- billion2001 |>
  rename(age = demographics.age) |>
  filter(age != 0)
```

We tidied up company.type for use by merging misspelled or mistyped values. In the end, the three values are "new", "acquired", and "other", with "new" taking precedent over "acquired".

```{r}
#| label: clean-company.type

billion2001 <- billion2001 |>
  mutate(
    company.type = case_when(str_detect(company.type, "new") ~ "new",
                             str_detect(company.type, "quired") ~ "acquired",
                             TRUE ~ "other")
  )
```

How the individual is related to their company (e.g. CEO, investor, founder, etc.) is represented by company.relationship. We cleaned it up similarly to company.type. The unique relation types are founder, chairman, CEO, owner, investor, and relation, with founder taking precedent over CEO, CEO over the joint category of chairman/investor/owner, and chairman/investor/owner over relation. President was collapsed into CEO, and employee and lawyer were collapsed into relation. Two observations where company relation is unknown were filtered out.

```{r}
#| label: clean-relationship

billion2001 <- billion2001 |>
  rename(company.relation = company.relationship) |>
  mutate(
    company.relation = if_else(str_detect(company.relation, "founder"), "founder", company.relation),
    company.relation = if_else(str_detect(company.relation, "president"), "ceo", company.relation),
    company.relation = if_else(str_detect(company.relation, "CEO"), "ceo", company.relation),
    company.relation = if_else(str_detect(company.relation, "Officer"), "ceo", company.relation),
    company.relation = if_else(str_detect(company.relation, "man"), "chairman/investor/owner", company.relation),
    company.relation = if_else(str_detect(company.relation, "investor"), "chairman/investor/owner", company.relation),
    company.relation = if_else(str_detect(company.relation, "owner"), "chairman/investor/owner", company.relation),
    company.relation = if_else(str_detect(company.relation, "lawer"), "relation", company.relation),
    company.relation = if_else(str_detect(company.relation, "yee"), "relation", company.relation),
    company.relation = if_else(str_detect(company.relation, "group"), "relation", company.relation)
  ) |>
  filter(nchar(company.relation) > 2)
```

How old the company is may also give some insight. We calculated the age of the company by subtracting its founding year (from company.founded) from 2001, saving the results to a column named company.age. A single observation with 0 as a founding year was dropped.

```{r}
#| label: clean-founded

billion2001 <- billion2001 |> 
  filter(company.founded > 0) |>
  mutate(company.age = 2001 - company.founded)
```

Finally, the variable inherited is changed to a binary categorical variable. The end result is a dataset with 413 observations, each of which is a billionaire with information on them from the year 2001.

```{r}
#| label: summary

billion2001 <- billion2001 |>
  mutate(
    inherited = if_else(str_detect(wealth.how.inherited, "not inherited"), "Not inherited", "Inherited"),
    inherited = as.factor(inherited)
    )

glimpse(billion2001)
```

#### Preliminary visualizations

```{r}
#| label: mean-age

mean_age <- billion2001 |> 
  summarize(mean_age = mean(age)) |> pull(mean_age)
```

The mean age of the billionaires is around `r mean_age` years old. Below are graphs of the age distribution and wealth plotted against age. We see that age follows a bell curve distribution. The relationship between age and wealth seems weak visually; however, age is still an interesting variable to consider.

```{r}
#| label: vis-by-age
#| message: false

billion2001 |>
  ggplot(aes(x = age)) +
  geom_histogram(color = "black", fill = "steelblue") +
  labs(
    x = "Age (years)",
    y = "Number of billionaires",
    title = "Age distribution of billionaires"
  ) +
  theme_minimal()

billion2001 |> 
  ggplot(aes(x = age, y = wealth)) +
  geom_point() +
  labs(
    x = "Age (years)",
    y = "Wealth (in billions of dollars)",
    title = "Wealth plotted against age"
  ) +
  theme_minimal()
```

```{r}
#| label: mean-company-age

mean_comp_age <- billion2001 |> 
  summarize(mean_age = mean(company.age)) |> pull(mean_age)
```

The mean company age of the billionaires is `r mean_comp_age`. Below, company age is plotted in similar fashion. Most companies are younger than 100 years. It seems as if the older the company, the less wealthy the associated billionaire.

```{r}
#| label: vis-by-comp-age
#| message: false

billion2001 |>
  ggplot(aes(x = company.age)) +
  geom_histogram(color = "black", fill = "steelblue") +
  labs(
    x = "Company of age (years)",
    y = "Number of companies",
    title = "Company age distribution of billionaires"
  ) +
  theme_minimal()

billion2001 |> 
  ggplot(aes(x = company.age, y = wealth)) +
  geom_point() +
  labs(
    x = "Age of company (years)",
    y = "Wealth (in billions of dollars)",
    title = "Wealth plotted against company age"
  ) +
  theme_minimal()
```

```{r}
#| label: group-by-inheritance

yes_inherited <- billion2001 |>
  filter(inherited == "Inherited")

not_inherited <- billion2001 |>
  filter(inherited == "Not inherited")
```

Just how many billionaires inherit their wealth? The bar plot below shows that a while most of the billionaires do not inherit their wealth, the difference in number between the two groups does not seem too significant.

```{r}
#| label: vis-by-inherit

billion2001 |>
  ggplot(aes(x = inherited)) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(
    x = "Inheritance status",
    y = "Number of billionaires",
    title = "How many billionares inherit their wealth?"
  ) + 
  theme_minimal()
```

Below is a histogram displaying the distribution of total wealth when faceted by inheritance status. The data skews right for both distributions, suggesting that the majority of both types of billionaires have less than 20 billion USD, which is not a small amount by any means, but also not the most compared to some other billionaires

```{r}
#| label: vis-wealth

billion2001 |>
  ggplot(aes(x = wealth)) +
  geom_histogram(binwidth = 0.3, color = "black", fill = "steelblue") +
  facet_wrap(~inherited, ncol = 1) +
  labs(
    x = "Wealth (in billions of USD)",
    y = "Count of billionaires",
    title = "Distribution of total wealth",
  ) + 
  theme_minimal()
```

```{r}
#| label: mean-wealth-inheritance

billion2001 |> 
  group_by(inherited) |>
  summarize(mean_wealth = mean(wealth))
```

The mean wealth of those who inherit their wealth seems to be higher than those who didn't.

Next, we visualize the proportion of various company industries, as well as wealth distributions by industry.

```{r}
#| label: industry-vis
#| message: false

billion2001 |>
  group_by(industry) |>
  summarize(n = n()) |>
  ggplot(aes(x = "", y = n, fill = industry)) +
  geom_bar(stat="identity", width=1) + 
  coord_polar("y", start = 0) +
  labs(
    title = "Distribution of industry types",
    fill = "Company industry"
    ) +
  theme_void()

billion2001 |>
  ggplot(aes(x = wealth, y = industry, color = industry)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Billionaire worth by company industry",
       x = "Wealth (billions of dollars)", 
       y = "Industry"
       ) +
  theme_minimal()
```

The proportions and numbers are summarized below; again, they show that wealth varies between the industries.

```{r}
#| label: mean-by-industry

billion2001 |>
  group_by(industry) |>
  summarize(mean_wealth = mean(wealth),
            count = n(),
            percent_industry = (n()/nrow(yes_inherited))*100)
```

```{r}
#| label: mean-gdp

mean_gdp <- billion2001 |>
  summarize(mean_gdp = mean(location.gdp)) |> pull(mean_gdp)
```

The mean GDP of all the locations the billionaires are based is `r mean_gdp`. Below is a scatterplot displaying the relationship between GDP and wealth. It appears there may be an upward trend as the GDP of the billionaire's location increases.

```{r}
#| label: vis-by-gdp

billion2001 |>
  ggplot(aes(x = location.gdp, y = wealth)) +
  geom_point() +
labs(
  x = "Location GDP (dollars)",
  y = "Wealth (in billions of dollars)",
  title = "Billionaire wealth by GDP of location"
  ) +
  theme_minimal()
```

### **Multivariate linear regression**

Multivariate linear regression allows for prediction of the effects of several variables on a single response variable. We plan to use multivariate linear regression

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + company.relation + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.relation + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic4 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic5 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + company.type + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic6 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + company.type + industry + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic7 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + company.type + industry + inherited + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic8 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.relation + company.type + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-age", "-company.age", "-company.relation", "-company.type", "-industry", "-inherited", "-location.gdp", "-wealth.type") 
aic_values <- c(aicbase, aic1, aic2, aic3, aic4, aic5, aic6, aic7, aic8)
data.frame(variable_list, aic_values)
```

Removed company.relation

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.type + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic4 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic5 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + industry + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic6 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + industry + inherited + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic7 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + company.type + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-age", "-company.age", "-company.type", "-industry", "-inherited", "-location.gdp", "-wealth.type") 
aic_values <- c(aicbase, aic1, aic2, aic3, aic4, aic5, aic6, aic7)
data.frame(variable_list, aic_values)
```

Removed company.type

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + industry + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + inherited + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic4 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + location.gdp + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic5 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited + wealth.type, data = billion2001) |>
  glance() |> pull(AIC)

aic6 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-age", "-company.age", "-industry", "-inherited", "-location.gdp", "-wealth.type") 
aic_values <- c(aicbase, aic1, aic2, aic3, aic4, aic5, aic6)
data.frame(variable_list, aic_values)
```

Removed wealth.type

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic4 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic5 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ age + company.age + industry + inherited, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-age", "-company.age", "-industry", "-inherited", "-location.gdp") 
aic_values <- c(aicbase, aic1, aic2, aic3, aic4, aic5)
data.frame(variable_list, aic_values)
```

Removed age

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + industry + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic4 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ company.age + industry + inherited, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-company.age", "-industry", "-inherited", "-location.gdp") 
aic_values <- c(aicbase, aic1, aic2, aic3, aic4)
data.frame(variable_list, aic_values)
```

Removed company.age

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry + inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ inherited + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry + location.gdp, data = billion2001) |>
  glance() |> pull(AIC)

aic3 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry + inherited, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-industry", "-inherited", "-location.gdp") 
aic_values <- c(aicbase, aic1, aic2, aic3)
data.frame(variable_list, aic_values)
```

Removed location.gdp

```{r}
aicbase <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry + inherited, data = billion2001) |>
  glance() |> pull(AIC)

aic1 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ inherited, data = billion2001) |>
  glance() |> pull(AIC)

aic2 <- linear_reg() |>
  set_engine("lm") |>
  fit(wealth ~ industry, data = billion2001) |>
  glance() |> pull(AIC)

variable_list <- c("all included", "-industry", "-inherited") 
aic_values <- c(aicbase, aic1, aic2)
data.frame(variable_list, aic_values)
```

Removed inherited.

# Results

Based on our regression model, we can see that the optimal predictors of billionaire net worth remained the same for both billionaires that inherited their money and those that did not. We found that the best predictors were the billionaire's age and the industry of the billionaire's company. With that being said, even though these were the best predictors, they only yielded an $R^2$ of 0.19 and an adjusted $R^2$ of 0.12 for inherited billionaires and an $R^2$ of 0.05 and an adjusted $R^2$ of -0.02 for non-inherited billionaires. They are clearly better predictors for inherited billionaires than non-inherited billionaires, but are poor predictors in general. This suggests that a billionaire's worth cannot be strongly predicted by factors such as these, and that there are other attributes outside of this dataset that are contributing to their wealth.

Based on our histogram and analysis focusing on company industry, we can see that for both types of billionaires the most frequent industry is Consumer goods, retail, and restaurants, and the next highest is Money management. A notable difference though, is that there are 46 non-inherited billionaires compared to only 10 inherited billionaires from the technology industry (That's about 6% of billionaires from the inherited group compared to about 19% of the not inherited group). This occurrence stands to reason considering the tech industry is relatively new and filled with booming startups.

## 
