---
title: "Sevenr Project"
subtitle: "Report"
format: html
editor: visual
execute:
  echo: true
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
library(tidymodels)
```

# Introduction and data

```{r}
#| label: load-billion
billion <- read.csv("data/billionaires.csv")

glimpse(billion)
```

The dataset we are working with is a large listing of billionaires across the world along with information about them collected at three different time points. There are 2614 observations and 22 variables. Not every observation is a unique billionaire; many are repeated up to three times (one at each time point). In addition, not every 22 variable is statistically interesting; many, such as name, rank, and company.name are identifying variables. However, the other variables are statistically useful and interesting, and our goal is to investigate them.

The dataset was created in 2016 by Caroline Freund and Sarah Oliver, who are (or were) researchers at the Peterson Institute for International Economics. They compiled the list of individuals from Forbes billionaire lists dating from 1996 to 2015. A large percentage of the additional information collected was publicly available, coming from sources such as Forbes, news articles, and company websites.

One caveat about this dataset, and any data categorizing wealth, is that defining wealth is a subjective matter. For example, Forbes had to make many choices in determining who to include in the lists used as sources for this dataset. One such choice was to exclude billionaires that obtained wealth from official positions (e.g. high government roles, state leader positions, etc.). Another choice was to exclude billionaires who obtained their wealth via illegal methods. In addition, individuals and companies may fabricate what they publish about themselves, or simply characterize themselves subjectively. Thus, when drawing conclusions from analysis of this dataset, we must be careful not to generalize statements about legal nonpolitial billionaires to any person on the planet who accumulates wealth.

#### Relevant variables

As mentioned, there are 22 variables, of which some are identifying variables, and the rest are more useful or interesting. They are listed in the table:

| Variable name (unmodified)               | Meaning                                                                        |
|------------------------------------------|--------------------------------------------------------------------------------|
| company.relationship                     | relationship to the company (founder, etc.)                                    |
| company.sector                           | the sector of the economy to which the business belongs                        |
| company.type                             | type of business of the company                                                |
| demographics.age                         | age of the individual                                                          |
| location.citizenship                     | name of the country for which the individual has citizenship                   |
| location.country.code                    | 3-letter country code for which the individual has citizenship                 |
| location.gdp                             | gross domestic product of the country for which the individual has citizenship |
| location.region                          | part of the world where the individual lives                                   |
| [*wealth.worth.in.billions*]{.underline} | [*net worth of the individual in billions of USD*]{.underline}                 |
| wealth.how.category                      | where the individual's money came from                                         |
| wealth.how.industry                      | the specific industry the individual profited from                             |
| wealth.how.inherited                     | whether the individual's wealth was inherited or not                           |
| wealth.how.was.founder                   | whether the individual founded their company or not                            |

Of these variables, the wealth.worth.in.billions variable (underlined and italicized) makes for an interesting response variable; that is, we are interested in seeing how this variable could possibly be affected by the other variables. One variable we are especially curious about exploring, given today's discourse about where wealth comes from, is wealth.how.inherited; do the billionaires who inherit some wealth to begin with accumulate more differently from those who are "self-made"?

#### Research question and hypothesis

Thus, our research question is: "do the predictors of a linear regression modeling billionaire wealth change depending on if the wealth was inherited or not inherited?" That is, do the factors that are associated with higher levels of billionaire wealth change given that the billionaire had inherited money to begin with or not?

Our hypothesis is that there will be a difference between the model for inherited billionaires and the model for self-made billionaires. Which variables will or will not be included is rather unpredictable, as many factors may or may not play a true role in wealth accumulation. However, we predict that wealth.how.industry, which describes the industry sector, may be relevant, as it is generally well-known that technology is a rapidly growing sector.

<https://www.piie.com/publications/working-papers/origins-superrich-billionaire-characteristics-database?ResearchID=2917>

# Methodology

#### Data cleaning

Before any analysis, the dataset was tidied up.

One step was to filter for a single year instead of working with data over time. We chose the year 2001, because of the other variables, location.gdp was of interest, and 2001 is the most recent year for which there is data on GDP across the world (there is no GDP data for 2014).

```{r}
#| label: filter-2001
billion |> 
  group_by(year) |> 
  summarize(mean_gdp = mean(location.gdp))

billion2001 <- billion |>
  filter(year == 2001) 
```

Another variable that is of interest is wealth.how.industry, whose values are strings representing the industries that made the billionaires wealthy. First, we renamed the variable to industry. Then, after noticing that several industries are highly related, we combined them together. For example, "Venture capital", "Hedge funds", "Diversified financial", and "Private equity/leveraged buyout" all fit into the "Money management" industry.

```{r}
#| label: clean-industry

billion2001 <- billion2001 |>
  rename(industry = wealth.how.industry) |>
  mutate(
    industry = if_else(industry == 0, "Other", industry),
    industry = if_else(industry == "Energy" | industry == "Mining and metals", "Energy, mining, and metals", industry),
    industry = if_else(str_detect(industry, "Technology"), "Technology", industry),
    industry = if_else(industry == "Diversified financial", "Money management", industry),
    industry = if_else(industry == "Hedge funds", "Money management", industry),
    industry = if_else(industry == "Venture Capital", "Money management", industry),
    industry = if_else(industry == "Private equity/leveraged buyout", "Money management", industry),
    industry = if_else(industry == "Money Management", "Money management", industry),
    industry = if_else(industry == "Constrution" | industry == "Real Estate", "Real estate, construction", industry),
    industry = if_else(industry == "Consumer" | industry == "Retail, Restaurant", "Consumer goods, retail, restaurants", industry)
  )
```

Are the billionaires old or young? demographics.age is another interesting variable; however, several billionaires have an age of 0 listed. We found out that several of the individuals with listed age 0 had died before 2001. Because researching dozens of individual death dates or ages demands excessive effort, we decided to filter out any age with 0 after renaming the variable to just 'age'.

```{r}
#| label: clean-age

billion2001 <- billion2001 |>
  rename(age = demographics.age) |>
  filter(age != 0)
```

Company type may also be relevant to wealth accumulation. Thus, we tidied up company.type for use by merging misspelled or mistyped values. In the end, the three values are "new", "acquired", and "other", with "new" taking precedent over "acquired".

```{r}
#| label: clean-company.type

billion2001 <- billion2001 |>
  mutate(
    company.type = case_when(str_detect(company.type, "new") ~ "new",
                             str_detect(company.type, "quired") ~ "acquired",
                             TRUE ~ "other")
  )
```

How the individual is related to their company (e.g. CEO, investor, founder, etc.) is represented by company.relationship. We renamed the variable to company.relation and cleaned it up similarly to company.type. The unique relation types are founder, chairman, CEO, owner, investor, and relation, with founder taking precedent over CEO, CEO over the joint category of chairman/investor/owner, and chairman/investor/owner over relation.

```{r}
#| label: clean-relationship

billion2001 <- billion2001 |>
  rename(company.relation = company.relationship) |>
  mutate(company.relation = case_when(str_detect(company.relation, "founder") ~ "founder",
                                      str_detect(company.relation, "CEO") ~ "ceo",
                                      TRUE ~ company.relation)
                                      )
  
```

comapny.relation

company.founded

#### Preliminary visualizations

#### Methods

Multivariate linear regression.

Model building

Other tools

## Results

Two (or more) linear regression models

```{r}
#| label: grouping by inheritance
inheritance_grouping <- billion2001 |>
  mutate(inherited = if_else(str_detect(wealth.how.inherited, "not inherited"), "not inherited", "inherited"))

yes_inherited <- inheritance_grouping |>
  filter(inherited == "inherited")

not_inherited <- inheritance_grouping |>
  filter(inherited == "not inherited")
```

```{r}
#| label: location-regression

#regression by location.gdp for both groups
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = billion2001) |>
  tidy()
 
billion2001 |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression for location.gdp for inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = yes_inherited) |>
  tidy()
 
yes_inherited |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 

#regression for location.gdp for not inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ location.gdp, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = location.gdp, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

```{r}
#| label: industry-regression

#regression by industry for both groups
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = billion2001) |>
  tidy()
 
billion2001 |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression by industry for inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = yes_inherited) |>
  tidy()
 
yes_inherited |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
 
#regression by industry for not inherited
linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ industry, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = industry, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

```{r}
#| label: age-regression

#regression by age for both groups
linear_reg() |>
    set_engine("lm") |>
    fit(wealth.worth.in.billions ~ demographics.age, data = billion2001) |>
    tidy()
 
billion2001 |>
    ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
    geom_point() +
    geom_smooth(method = "lm", se = F) 
 
#regression by age for inherited
linear_reg() |>
    set_engine("lm") |>
    fit(wealth.worth.in.billions ~ demographics.age, data = yes_inherited) |>
    tidy()
 
 yes_inherited |>
    ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
    geom_point() +
    geom_smooth(method = "lm", se = F) 
 
#regression by age for not inherited
 linear_reg() |>
  set_engine("lm") |>
  fit(wealth.worth.in.billions ~ demographics.age, data = not_inherited) |>
  tidy()
 
not_inherited |>
  ggplot(aes(x = demographics.age, y = wealth.worth.in.billions)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) 
```

## Changelog

4/3:

-   filtered year and variables (variable_filter)

-   grouped by inheritance (inheritance_grouping, yes_inherited, not_inherited)

-   regressions by location, age, sector; univariate models from total, then individual group data frames

4/5:

-   renamed variable_filter to billion2001, renamed wealth.how.industry to industry

-   removed selecting variables (aka leaving all variables in)

-   added comments

-   commented out glimpse(billion)

-   cleaned up and combined industry levels (check underneath for groupings)

-   changed regression by company.sector to regression by industry

-   
